Tabular Constraint Learning

### 2016-03-31 Paper/ECAI/tabular.tex
added references
updating the paper
added short related work annotation

\documentclass{ecai}
\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage[dvipsnames]{xcolor}
\newcommand{\sergey}[1]{\textcolor{magenta}{{\sc Sergey} #1}\xspace}

@@

\author{Name1 Surname1 \and Name2 Surname2 \and Name3 Surname3 \institute{KU Leuven,Belgium, email: firstname.lastname@kuleuven} }

\maketitle
\bibliographystyle{ecai}

@@

\section{Related Work}
\sergey{what else should be in the related work?}
flashfill

sketch

tabular?

\bibliography{references}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass{ecai}
\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage[numbers]{natbib}
\usepackage{notoccite}

\usepackage[dvipsnames]{xcolor}
\newcommand{\sergey}[1]{\textcolor{magenta}{{\sc Sergey} #1}\xspace}

@@

\author{Name1 Surname1 \and Name2 Surname2 \and Name3 Surname3 \institute{KU Leuven, Belgium, email: firstname.lastname@kuleuven} }

\maketitle

@@

\section{Related Work}
\sergey{ECAI reference style file ignores their guideline and their guideline ignores what is written in the guidelines!}
flashfill, flashextract, flashmeta \cite{flashfill,flashextract,flashmeta}
\begin{itemize}
  \item their supervised vs our unsupervised approach
  \item they look for a single ``smallest'' solution, we enumerate them all
  \item they are looking for a function, we solve constraint satisfaction problems
  \item we do not assume classic row based data layout, we work in the tabular setting
\end{itemize}

sketch \cite{sketch}
\begin{itemize}
  \item look for a constant that would fill in the gap in a program
  \item tailored for programming languages
  \item similar to model checking
  \item looks for a single solution
  \item similar to constraint satisfaction and sat, where one is interested in a single assignment that works for any potential input
\end{itemize}

tabular \cite{tabular}
\begin{itemize}
  \item language based on the excel tables that specify probabilistic models
  \item a system for probabilistic inference and similarity mostly in the usage of excel
  \item probabilistic constraint satisfaction (?) and graphical models
  \item single solution again
\end{itemize}

modelseeker \cite{modelseeker} \sergey{Samuel, Luc, probably you would need elaborate here more in details}

\begin{itemize}
  \item not designed for excel-like data representation (type consistency, groups, etc)
  \item not designed for excel-like constraints (lookups, conditional ifs, etc)
  \item does not support user extensions (?)
\end{itemize

claudien \cite{claudien} \sergey{Samuel, Luc, you would need to help with this one}

\bibliographystyle{ecai}
\bibliography{references}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
